\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage[margin=0.3in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}
\setlist{nosep, leftmargin=*, itemsep=0pt, topsep=0pt, parsep=4pt}

\pagestyle{empty}

\begin{document}

\begin{center}
{\LARGE \textbf{Yicheng (Albert) Zhan}}\\[0.3em]
E-mail: yicheng\_zhan2001@outlook.com | \href{https://scholar.google.com/citations?user=x2ptSYUAAAAJ}{Google Scholar} | \href{https://github.com/AlberTgarY}{GitHub}
\end{center}

\section*{EDUCATION}
\textbf{Ph.D. candidate (3rd year)} \hfill \textbf{Jan. 2024 - Now} \\
\textbf{University College London - Computational Light Laboratory} \hfill \textbf{London, United Kingdom}\begin{itemize}
\item \textbf{Core Fields}: Computer-Generated Holography, Computer Graphics, Computational Displays.
\item \textbf{Thesis Title}: Advanced Algorithms for Next-Generation Computational Displays. (\textbf{Mentor}: Assoc. Prof. Kaan Akşit)
\end{itemize}

\textbf{M.Sc. in Computer Graphics and Vision Imaging} \hfill \textbf{Sep. 2021 - Sep. 2022} \\
\textbf{University College London} \hfill \textbf{London, United Kingdom}\begin{itemize}
\item \textbf{Graduate Result}: First Class Distinction
\item \textbf{Dissertation Title}: Urban Semantic Understanding. (\textbf{Supervisor}: Assoc. Prof. Melinos Averkiou)
\end{itemize}

\textbf{B.Sc. (Hons) in Software Engineering and Computer Science} \hfill \textbf{Sep. 2018 - Sep. 2021} \\
\textbf{King's College London} \hfill \textbf{London, United Kingdom}\begin{itemize}
\item \textbf{Graduate Result}: First Class Honors
\item \textbf{Dissertation}: Slackbot Security Evaluation. (\textbf{Supervisor}: Prof. Jose Such)
\end{itemize}

\section*{WORK EXPERIENCE}
\textbf{Research Scientist Intern - Optics Optimization} \hfill \textbf{Mar. 2026 - Now} \\
Meta Reality Lab (Supervisor: Dr. Yijing Fu) \hfill \textbf{Redmond, United States}
\vspace{0.01em}

\textbf{Research Scientist Intern - Neural Representation} \hfill \textbf{Apr. 2025 - Sep. 2025} \\
Huawei Technologies Research \& Development (UK) Ltd (Supervisor: Dr. Arthur Moreau) \hfill \textbf{London, United Kingdom}
\vspace{0.01em}

\textbf{Research Assistant - Crime Linkage Analysis} \hfill \textbf{Jul. 2023 - Jan. 2025} \\
Imperial College London (Supervisor: Assoc. Prof. Dalal Alrajeh) \hfill \textbf{London, United Kingdom}
\vspace{0.01em}

\textbf{Research Assistant - Computer Vision} \hfill \textbf{Apr. 2023 - Dec. 2023} \\
University of Leeds \hfill \textbf{Leeds, United Kingdom}
\vspace{0.01em}

\textbf{AI Programmer Intern} \hfill \textbf{Jul. 2020 - Sep. 2020} \\
Microsoft China \hfill \textbf{Beijing, China}
\vspace{0.01em}

\section*{PUBLICATIONS}
\begin{itemize}
\item Xiaoyue Fan, \textbf{Yicheng Zhan}, Amrita Mazumdar, and Kaan Akşit, \textit{``Compressing Double-Phase Holograms using 2D Gaussians''} \textit{Eurographics 2026 Posters}. (\href{https://complightlab.com/publications/compressing_double_phase_gs/}{Web})
\item \textbf{Yicheng Zhan}, Fahim Ahmed, Amy Burrell, Matthew J. Tonkin, Sarah Galambos, Jessica Woodhams, and Dalal Alrajeh, \textit{``Enhancing Binary Encoded Crime Linkage Analysis Using Siamese Network''} \textit{AAAI 2026}. (\href{https://ojs.aaai.org/index.php/AAAI/article/view/41309}{Web})
\item \textbf{Yicheng Zhan}, Xiangjun Gao, Long Quan, and Kaan Akşit, \textit{``Complex-Valued 2D Gaussian Representation for Computer-Generated Holography''} ArXiv Preprint 2025. (In preparation) (\href{https://arxiv.org/abs/2511.15022}{Web})
\item Zicong Peng, \textbf{Yicheng Zhan}, Josef Spjut, and Kaan Akşit, \textit{``Assessing Learned Models for Phase-only Hologram Compression''} \textit{ACM SIGGRAPH 2025 Posters}. (\href{https://complightlab.com/publications/assess_hologram_compression/}{Web})
\item \textbf{Yicheng Zhan}, Dong-Ha Shin, Seung-Hwan Baek, and Kaan Akşit, \textit{``Complex-Valued Holographic Radiance Fields''} \textit{ACM Transactions on Graphics (presented in SIGGRAPH 2026)}. (\href{https://complightlab.com/publications/complex_valued_holographic_radiance_fields/}{Web})
\item \textbf{Yicheng Zhan}, Qi Sun, Liang Shi, Wojciech Matusik, and Kaan Akşit, \textit{``Configurable Holography: Towards Display and Scene Adaptation''} ArXiv Preprint 2024. (In preparation) (\href{https://arxiv.org/abs/2405.01558}{Web})
\item \textbf{Yicheng Zhan}, Koray Kavaklı, Hakan Urey, Qi Sun, and Kaan Akşit, \textit{``AutoColor: Learned Light Power Control for Multi-Color Holograms''} \textit{SPIE VR/AR/MR 2024}. (\href{https://complightlab.com/autocolor_/}{Web})
\item Chuanjun Zheng, \textbf{Yicheng Zhan}, Liang Shi, Ozan Cakmakci and Kaan Akşit, \textit{``Focal Surface Holographic Light Transport using Learned Spatially Adaptive Convolutions''} \textit{ACM SIGGRAPH ASIA 2024 Tech Comm.}. (\href{https://complightlab.com/publications/focal_surface_light_transport/}{Web})
\end{itemize}

\section*{SKILLS}
Language skills: English (fluent), Chinese (native), Spanish (Intermediate)

Interests: Compose Hiphop Music, Sleep, Long-distance Running.

\end{document}
